---
title: "Covariate sensitivity analysis. Population PK/PD analysis of axatilimab, IV-SC bridging."
subtitle: "Studies SNDX-6352-0001, -0502, -0503, -0504, INCA36176-101, -102"
author: "M&S Decisions, `r Sys.Date()`"

output: 
    bookdown::html_document2:
      toc: true
      toc_depth: 5
      toc_float:
        collapsed: true
        smooth_scroll: false
      number_sections: true
      code_folding: hide
      fig_width: 10
      fig_height: 7
      fig_caption: true
      
    officedown::rdocx_document:
      reference_docx: document_template.docx
---

```{r load-packages-and-functions, include = FALSE}
rm(list=ls())
set.seed(123456)
library(rxode2)
library(sjlabelled)
library(haven)
library(tidyverse)
library(flextable)
library(officer)
library(officedown)
library(bookdown)
library(table1)
library(DT)
library(cowplot)
library(ggpubr)

theme_set(theme_bw())
theme_update(panel.grid.minor = element_blank())
MSDcol <- c("#1a1866", "#f2b93b", "#b73b58", "#a2d620", "#5839bb", "#9c4ec7", "#3a6eba", "#efdd3c", "#69686d")

set_flextable_defaults(
  font.family = "Arial",
  font.size = 8,
  theme_fun = "theme_vanilla",
  table.layout = "autofit"
  )

funSum_sim <- list(mean   = ~mean(.),
                   median = ~median(.),
                   min    = ~min(.),
                   max    = ~max(.),
                   sd     = ~sd(.), 
                   P025   = ~quantile(., 0.025),
                   P05    = ~quantile(., 0.05),
                   P10    = ~quantile(., 0.10),
                   P15   = ~quantile(., 0.15),
                   P25    = ~quantile(., 0.25),
                   P75    = ~quantile(., 0.75),
                   P85   = ~quantile(., 0.85),
                   P90    = ~quantile(., 0.90),
                   P95    = ~quantile(., 0.95),
                   P975   = ~quantile(., 0.975),
                   geom_mean = ~exp(mean(log(.), na.rm = T)),
                   CV     = ~sd(., na.rm = T)/mean(., na.rm = T)*100)

funSum_av <- list(mean   = ~mean(.),
                  median   = ~median(., na.rm = T))

funSum_exp <- list(`Cavg, nmol/L`   = ~mean(.),
                   `Cmin, ug/mL`    = ~min(.),
                   `Cmax, nmol/L`    = ~max(.))

fun_ForSim <- function(mod_i, et_i, s_times_i = NULL, vars_i = NULL, theta_i = NULL, omega_i = NULL, sigma_i = NULL, thetamat_i = NULL, 
                       thlow = -Inf, nrep = 1,
                       aggr_id = F, aggr_tot = F, keep = NULL, cov_i = NULL, addcov = T, ncores = 1){
  et_i_m <- et_i %>% et()
  if(!is.null(s_times_i)){ et_i_m <- et_i_m %>% add.sampling(s_times_i) }
  if(!is.null(cov_i)){
    if(!is.null(s_times_i)){ 
      et_i_cov <- et_i %>% select(id, all_of(cov_i)) %>% unique()
      et_i_m <- et_i_m %>% as_tibble() %>% left_join(et_i_cov, by = "id")
    } else {
      et_i_cov <- et_i %>% select(all_of(cov_i))
      et_i_m <- et_i_m %>% bind_cols(et_i_cov)
    }
  }
  sim_i <- rxSolve(mod_i, events = et_i_m, params = theta_i, omega = omega_i, sigma = sigma_i, thetaMat = thetamat_i, nStud = nrep, thetaLower = thlow, covsInterpolation = "locf", cores = ncores, addCov = F)
  
  sim_i_ind <- sim_i %>% as_tibble()
  if(!"id" %in% colnames(sim_i_ind)){ sim_i_ind <- mutate(sim_i_ind, id = 1) }
  if(!"sim.id" %in% colnames(sim_i_ind)){ sim_i_ind <- mutate(sim_i_ind, sim.id = 1) }
  sim_i_ind <- sim_i_ind %>% gather("VAR", "VALUE", -id, -sim.id, -time)
  if(!is.null(vars_i)){sim_i_ind <- sim_i_ind %>% filter( VAR %in% vars_i )}
  
  sim_i_aggr_id <- NULL; sim_i_aggr_tot <- NULL
  sim_i_out <- list(IND = sim_i_ind, AGGR_ID = sim_i_aggr_id, AGGR_TOT = sim_i_aggr_tot)
  
  if(aggr_id){
    sim_i_out$AGGR_ID <- sim_i_ind %>% group_by(id, time, VAR) %>% summarise_at(vars(VALUE), funSum_sim) %>% ungroup()
  }
  
  if(aggr_tot){
    sim_i_out$AGGR_TOT <- sim_i_ind %>% group_by(time, VAR) %>% summarise_at(vars(VALUE), funSum_sim) %>% ungroup()
  }
  
  if(!is.null(keep)){
    sim_i_out <- sim_i_out %>% map(function(x){
      if(!is.null(x) & "id" %in% colnames(x)){left_join(x, unique(select(et_i, id, all_of(keep))), by = "id")}
    })
  }
  
  if(addcov & !is.null(cov_i)){
    sim_i_out <- sim_i_out %>% map(function(x){
      if(!is.null(x) & "id" %in% colnames(x)){left_join(x, unique(select(et_i_cov, id, all_of(cov_i))))}
    })
  }
  return(sim_i_out)
}

fun_EtCC <- function(et_base_i, cc_ds_i, cat = F){
  et_scov_i <- unique(cc_ds_i$COV) %>% map(function(n){
    cc_ds_n <- cc_ds_i %>% filter(COV == n)
    
    et_scov_n <- seq(nrow(cc_ds_n)) %>% map_dfr(function(m){
      row_m <- cc_ds_n %>% filter(row_number() == m)
      
      et_scov_m <- et_base_i %>% 
        mutate_at(vars(all_of(row_m$COV)), function(k){k = row_m$COVVAL})
      if(!cat){
        et_scov_m <- et_scov_m %>% bind_cols(select(row_m, COV, PAR, BTR, KEY, COVVAL, BCOVVAL))
      } else {
        et_scov_m <- et_scov_m %>% bind_cols(select(row_m, COV, PAR, KEY, COVVAL, CATDES))
      }
      
      return(et_scov_m)
      
    }) %>% mutate(id = row_number())
    
    return(et_scov_n)
  })
  names(et_scov_i) <- unique(cc_ds_i$COV)
  return(et_scov_i)
}

fun_CovSens <- function(et_sim_i, cat = F, expos = F, covs_i = NULL, nsim = 1000, stime_exp = NULL, var_exp = "Cc_mgL"){
  keep_i <- c("Regimen", "KEY", "COV", "COVVAL")
  if(!cat){
    keep_i <- c(keep_i, "BTR", "BCOVVAL")
  } else {
    keep_i <- c(keep_i, "CATDES")
  }

  sens_i <- et_sim_i %>% map_dfr(function(et_i){
    if(!expos){
      par_i <- unique(et_i$PAR)
      if(is.list(par_i)){ par_i <- par_i[[1]] }
      sim_i <- fun_ForSim(mod_fin, et_i, 0, vars_i = par_i, theta_i = par_fin_tv, thetamat_i = m_theta_norm_pop, cov_i = covs_i, nrep = nsim, keep = keep_i)$IND
    } else {
      sim_i <- fun_ForSim(mod_fin, et_i, stime_exp, vars_i = var_exp, theta_i = par_fin_tv, thetamat_i = m_theta_norm_pop, cov_i = covs_i, nrep = nsim, keep = keep_i, ncores = max(1, parallel::detectCores()-2))$IND %>% 
        group_by_at(vars(all_of(c("sim.id", keep_i, covs_i)))) %>% summarise_at(vars(VALUE), funSum_exp) %>% ungroup() %>% 
        gather("VAR", "VALUE", -all_of(c("sim.id", keep_i, covs_i)))
    }
    
    sim_i_ref <- sim_i %>% filter(KEY == "REF" | KEY == 1) %>% select(sim.id, VAR, REFVAL = VALUE)
    sim_i_ch <- sim_i %>% filter(KEY != "REF" & KEY != 1) %>% left_join(sim_i_ref, by = c("sim.id", "VAR")) %>% 
      mutate(PCH = 100*(VALUE - REFVAL)/REFVAL)
    
    out_i <- sim_i_ch %>% group_by_at(vars(all_of(c("VAR", keep_i, covs_i)))) %>% summarise_at(vars(PCH), funSum_sim) %>% ungroup()
  }) %>% left_join(nice_names, by = "COV")
  
  if(!cat){
    sens_out <- sens_i %>% select(NICEN, VAR, KEY, mean:P975, Regimen, COVVAL:BCOVVAL) %>% mutate(KEY = ifelse(KEY == "LP", "10th perc.", "90th perc."), LAB = str_c(NICEN, "\n", KEY, " (", round(BCOVVAL, 1), ")"))
  } else {
    sens_out <- sens_i %>% select(NICEN, VAR, CATDES, mean:P975, Regimen) %>% mutate(LAB = str_c(NICEN, " (", CATDES, ")"))
  }
  sens_out <- sens_out %>% mutate_at(vars(mean:P975), function(p){p/100+1})
  return(sens_out)
}

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE, fig.cap = TRUE, fig.align = "center")

if (!knitr::is_html_output()) {
  run_num_tab <- run_autonum(seq_id = "Table", pre_label = "Table ", bkm = "anytable")
  run_num_fig <- run_autonum(seq_id = "Figure", pre_label = "Figure ", bkm = "anyfigure")
}

```

```{r extract-parameters}
path_project <- "poppkpd/final-model/model-final-v2/"
par_fin <- read_csv(str_c(path_project, "/populationParameters.txt"), col_types = cols())
path_to_save <- "poppkpd/interim-datasets/"

### Population parameters
par_pop <- par_fin %>% filter(str_detect(parameter, "_pop")) %>% select(parameter, value) %>% deframe()
par_fin_tv <- par_fin %>% filter(str_detect(parameter, "_pop$") | str_detect(parameter, "^beta_")) %>% select(parameter, value) %>% 
  mutate(value = case_when(
    str_detect(parameter, "_pop$") & parameter == "Fbio_pop" ~ logit(value), 
    str_detect(parameter, "_pop$") & parameter != "Fbio_pop" ~ log(value), 
    T ~ value)) %>% 
  deframe()

### Reconstruct omega matrix
d_omega <- par_fin %>% filter(str_detect(parameter, "omega_"))
m_omega <- diag(d_omega$value, ncol = length(d_omega$value))
colnames(m_omega) <- d_omega$parameter; rownames(m_omega) <- d_omega$parameter
m_omega_full <- m_omega

corr_set <- par_fin %>% filter(str_detect(parameter, "corr_"))
if(nrow(corr_set) > 0){
  corr_set <- corr_set %>% 
    separate(parameter, c("TYPE", "PAR1", "PAR2"), "_") %>% 
    select(PAR1, PAR2, value) %>% 
    mutate_at(vars(PAR1, PAR2), function(x){str_c("omega_", x)})
  
  omega_corr <- m_omega
  diag(omega_corr) <- rep(1, ncol(m_omega))
  for(i in 1:nrow(corr_set)){
    cs_i <- corr_set[i, ]
    omega_corr[cs_i$PAR1, cs_i$PAR2] <- cs_i$value
    omega_corr[cs_i$PAR2, cs_i$PAR1] <- cs_i$value
  }
  
  m_omega_full <- m_omega %*% omega_corr %*% m_omega
}


### Reconstruct residual error model matrix
d_reserr <- par_fin %>% filter(!str_detect(parameter, "_pop|omega_|corr_|beta_"))
m_reserr <- diag(d_reserr$value, ncol = length(d_reserr$value))
colnames(m_reserr) <- d_reserr$parameter; rownames(m_reserr) <- d_reserr$parameter


### Establish uncertainty distribution
est_covmat <- read_csv(str_c(path_project, "FisherInformation/covarianceEstimatesSA.txt"),
                       col_names = F, col_types = cols())

m_theta_norm <- est_covmat %>% select_if(is.numeric) %>% as.matrix()
colnames(m_theta_norm) <- est_covmat$X1; rownames(m_theta_norm) <- est_covmat$X1
m_theta_norm_pop <- m_theta_norm[str_detect(rownames(m_theta_norm), "_pop|beta_"), str_detect(colnames(m_theta_norm), "_pop|beta_")]
```

```{r compile-the-model}
mod_fin <- RxODE({
  # Dose in mg
  # Time in hours
  
  ### Parameters
  # Typical values
  Tlag_pop = 0.42644047;
  ED50_po = 3.92413811;
  # Fbio_pop = -1.03162159;
  ka_pop = -3.69962616;
  kdec_pop = -4.14187971;
  Vd_pop = 1.25397100;
  CL_pop = -5.06690320;
  Q_pop = -4.62217469;
  Vp_pop = 0.79821986;
  Vmax_pop = -1.00374240;
  Kd_PK_pop = 0.04615490;
  Nh_PK_pop = 0.79810778;
  BL_CSF1_pop =  -4.72238811;
  kdeg_CSF1_pop = -6.62985098;
  k_ada_pop = 0.01642367;
  
  # Random effects
  omega_ka = 0;
  omega_Tlag = 0;
  omega_Vd = 0;
  # omega_Fbio = 0;
  omega_kdec = 0;
  omega_ED50 = 0;
  omega_CL = 0;
  omega_Vmax = 0;
  omega_BL_CSF1 = 0;

  # Covariate coefficient
  beta_Vd_LOG_WT = 0.77478986;
  beta_CL_LOG_CSF1 = 0.91389039;
  beta_BL_CSF1_LOG_CSF1 = 0.74539833;
  beta_Vd_ASSAY_2 = 0.18087319;
  beta_CL_ASSAY_2 = 1.74272531;
  beta_Vmax_ASSAY_2 = -0.28183421;
  beta_BL_CSF1_ASSAY_2 = -0.11744836;
  
  # Categorical covariates assignment
  beta_Vd_ASSAY = 0;
  beta_CL_ASSAY = 0;
  beta_Vmax_ASSAY = 0;
  beta_BL_CSF1_ASSAY = 0;
  if(ASSAY == "2"){beta_Vd_ASSAY = beta_Vd_ASSAY_2};
  if(ASSAY == "2"){beta_CL_ASSAY = beta_CL_ASSAY_2};
  if(ASSAY == "2"){beta_Vmax_ASSAY = beta_Vmax_ASSAY_2};
  if(ASSAY == "2"){beta_BL_CSF1_ASSAY = beta_BL_CSF1_ASSAY_2};
  
  beta_ADA = 0;
  if(ADACAT == "1"){beta_ADA = 1};
  
  # Residual error
  b1 = 0;
  b2 = 0;

  # Transformation
  Tlag_tv = exp(Tlag_pop);
  # Fbio_tv = exp(Fbio_pop)/(1 + exp(Fbio_pop));
  ED50_tv = exp(ED50_pop);
  ka_tv = exp(ka_pop);
  kdec_tv = exp(kdec_pop);
  Vd_tv = exp(Vd_pop);
  CL_tv = exp(CL_pop);
  Q_tv = exp(Q_pop);
  Vp_tv = exp(Vp_pop);
  Vmax_tv = exp(Vmax_pop);
  Kd_PK_tv = exp(Kd_PK_pop);
  Nh_PK_tv = exp(Nh_PK_pop);
  BL_CSF1_tv = exp(BL_CSF1_pop);
  kdeg_CSF1_tv = exp(kdeg_CSF1_pop);
  k_ada_tv = exp(k_ada_pop);
  
  k_ada = k_ada_tv;
  ED50 = ED50_tv*exp(omega_ED50);
  # Fbio = exp(Fbio_pop + omega_Fbio)/(1 + exp(Fbio_pop + omega_Fbio));
  Tlag = Tlag_tv*exp(omega_Tlag);
  ka = ka_tv*exp(omega_ka);
  kdec = kdec_tv*exp(omega_ED50);
  Vd = Vd_tv*exp(omega_Vd + beta_Vd_LOG_WT*LOG_WT + beta_Vd_ASSAY);
  CL = CL_tv*exp(omega_CL + beta_CL_LOG_CSF1*LOG_CSF1 + beta_CL_ASSAY)*(1 + k_ada*beta_ADA);
  Q = Q_tv;
  Vp = Vp_tv;
  Vmax = Vmax_tv*exp(omega_Vmax + beta_Vmax_ASSAY);
  Kd_PK = Kd_PK_tv;
  Nh_PK = Nh_PK_tv;
  BL_CSF1 = BL_CSF1_tv*exp(omega_BL_CSF1 + beta_BL_CSF1_LOG_CSF1*LOG_CSF1 + beta_BL_CSF1_ASSAY);
  kdeg_CSF1 = kdeg_CSF1_tv;
  
  ### Priors
  Kd_CSF1 = 0.048 ;   					# nM for CSF1 Rouseel et al. (1988) Cell
  
  ### Explicit functions
  Cc = Ac/Vd;   # ug/L
  Cp = Ap/Vp;   # ug/L
  
  convF_PK = 0.01/1.5;     			# ng/mL -> nM for mAb MW 150 kDa
  Cc_nM  = Cc*convF_PK;    			# nM
  Cc_mgL = Cc/1000;					# mg/L
  
  convF_CSF1= 0.01/0.6; 				# ng/mL -> nM for CSF-1 MW 60 kDa
  CSF1_ngmL = CSF1/convF_CSF1;			# ng/mL
  CSF1_pgmL = 1000*CSF1_ngmL; 			# pg/mL
  
  
  C1 = (Cc_nM/Kd_PK)^Nh_PK/(1 + (Cc_nM/Kd_PK)^Nh_PK + CSF1/Kd_CSF1);  # Complex1 part 
  C2 = (CSF1/Kd_CSF1)/(1 + (Cc_nM/Kd_PK)^Nh_PK + CSF1/Kd_CSF1);       # Complex2 part
  BL_C2 = (BL_CSF1/Kd_CSF1)/(1 + BL_CSF1/Kd_CSF1);
  
  ksyn_CSF1 = kdeg_CSF1*BL_CSF1 + Vmax*BL_C2;

  ### Initial conditions
  Ad(0) = 0; 
  Ac(0) = 0;         
  Ap(0) = 0;         
  CSF1(0) = BL_CSF1; # nM

  ### ODEs
  d/dt(Ad) = - ka*Ad*exp(-kdec*LDOSE);
  d/dt(Ac) = ka*Ad*exp(-kdec*LDOSE) - CL*Cc - Q*(Cc - Cp) - (Vmax*C1/convF_PK)*Vd;
  d/dt(Ap) = Q*(Cc - Cp);
  d/dt(CSF1) = ksyn_CSF1 - kdeg_CSF1*CSF1 - Vmax*C2;

  ### Other
  alag(Ad) = Tlag;
  f(Ad) = 1000*LDOSE/(ED50 + LDOSE);
  f(Ac) = 1000;
  
  DV1 = Cc_mgL*(1 + b1);
  DV2 = CSF1_ngmL*(1 + b2);
})

```

```{r user-input}
data_fin <- read_csv("./poppkpd/interim-datasets/poppkpdall_mod_102m_ref2.csv", na = ".", col_types = cols(), guess_max = 10000) %>% 
  mutate(ADACAT = as.character(ADACAT), ASSAY = as.character(ASSAY))
# simpp <- read_xpt("../datasets/simpp.xpt")

# Categorical: CMSTCAT, STUDYID
# Continuous: LOG_WT, LOG_LDH, LOG_MONO, LOG_CSF1, NCMCT

cont_cov <- tribble(
  ~TR,           ~BTR,      ~PAR,
  "LOG_WT",      "WTBL",    c("Vd"),
  # "LOG_LDH",     "LDHBL",   c("CL", "BL_CSF1"),
  # "LOG_MONO",    "MONOBL",  c("CL"),
  "LOG_CSF1",    "CSF1BL",  c("BL_CSF1", "CL")
  # "NCMCT",       "NCMCBL",  c("Vmax"),
)
cat_cov <- tribble(
  ~COV,         ~COVVAL,             ~CATDES,  ~KEY, ~PAR,
  # "CMSTCAT",    "0",                 "No",     1,    c("Vd"),
  # "CMSTCAT",    "1",                 "Yes",    0,    c("Vd"),
  # "STUDYID",    "INCA34176-101",     "101",    1,    c("BL_CSF1"),
  # "STUDYID",    "SNDX-6352-0001",    "001",    0,    c("BL_CSF1"),
  # "STUDYID",    "SNDX-6352-0502",    "502",    0,    c("BL_CSF1"),
  # "STUDYID",    "SNDX-6352-0503",    "503",    0,    c("BL_CSF1"),
  # "STUDYID",    "SNDX-6352-0504",    "504",    0,    c("BL_CSF1"),
  "ADACAT",     "0",                 "No",     1,    c("CL"),
  "ADACAT",     "1",                 "Yes",    0,    c("CL"),
  "ASSAY",      "1",                 "Other",  1,    c("Vd", "CL", "Vmax", "BL_CSF1"),
  "ASSAY",      "2",                 "102",    0,    c("Vd", "CL", "Vmax", "BL_CSF1")
  )

nice_names <- tribble(
 ~COV,        ~NICEN,
 "LOG_WT",    "Weight, kg",
 # "LOG_LDH",   "LDH, U/L",
 # "LOG_MONO",  "Monocytes, cells/nL",
 "LOG_CSF1",  "CSF-1, ng/L",
 # "NCMCT",     "NCMC, cells/uL",
 # "CMSTCAT",   "Corticosteroids",
 # "STUDYID",   "Study",
 "ADACAT",    "ADA status",
 "ASSAY",    "Assay",
)

ss_cycle <- 10
fun_stimes_ss <- function(k){c(
  k*4*7*24 + c(seq(0, 23.5, 1), seq(24, 335, 1)),
  k*4*7*24 + 2*7*24 + c(seq(0, 23.5, 1), seq(24, 335, 1))
)}
stimes_ss <- fun_stimes_ss(ss_cycle)

overwrite <- F
```

```{r covariate-distribution}
### Continuous covariates
ds_cc_tr <- data_fin %>% select(USUBJID, all_of(cont_cov$TR)) %>% unique() %>% 
  gather("TR", "TVALUE", -USUBJID) %>% left_join(cont_cov, by = "TR")

ds_cc_btr <- data_fin %>% select(USUBJID, all_of(cont_cov$BTR)) %>% unique() %>% 
  gather("BTR", "NVALUE", -USUBJID)
ds_cc_btr_av <- ds_cc_btr %>% group_by(BTR) %>% summarise_at(vars(NVALUE), funSum_av)

ds_cc <- ds_cc_tr %>% 
  left_join(ds_cc_btr, by = c("USUBJID", "BTR")) %>% 
  left_join(ds_cc_btr_av, by = "BTR") %>% 
  group_by(TR) %>% 
  mutate(
    LP = case_when(TR == "NCMCT" ~ quantile(NVALUE, 0.1) - median, T ~ log(quantile(NVALUE, 0.1)/median)), 
    UP = case_when(TR == "NCMCT" ~ quantile(NVALUE, 0.9) - median, T ~ log(quantile(NVALUE, 0.9)/median)), 
    REF = 0) %>% 
  ungroup()
ds_cc_reflab <- select(ds_cc, COV = TR, median) %>% unique() %>% left_join(nice_names, by = "COV") %>% summarise(OUT = str_c(str_c(NICEN, " = ", round(median, 1)), collapse = "\n")) %>% pull(OUT)

cc_to_test <- ds_cc %>% select(COV = TR, BTR, PAR, mean, median, LP, UP, REF) %>% unique() %>% 
  gather("KEY", "COVVAL", -COV:-median) %>% 
  mutate(BCOVVAL = case_when(COV == "NCMCT" ~ COVVAL + median, T ~ exp(COVVAL)*median))


### Categorical covariates
ds_catc <- data_fin %>% select(USUBJID, all_of(cat_cov$COV)) %>% unique()
catc_to_test <- ds_catc %>% select(-USUBJID) %>% gather("COV", "COVVAL") %>% unique() %>% left_join(cat_cov, by = c("COV", "COVVAL"))
```

```{r establish-event-tables}
### IV scenario
ev_t_base <- tribble(
  ~id, ~time, ~ii,  ~addl, ~dur,  ~cmt,  ~evid, ~Regimen,           ~Dose,
  1,   0,     336,  21,    0.5,   2,      1,     "0.3 mg/kg Q2W",   0.3
) %>% mutate(WTBL = unique(select(data_fin, USUBJID, WTBL)) %>% pull(WTBL) %>% median(), 
             LOG_WT = 0, LOG_CSF1 = 0, ADACAT = "0", ASSAY = "1",
             amt = Dose*WTBL, LDOSE = amt)

ets_cc <- fun_EtCC(ev_t_base, cc_to_test)
ets_catc <- fun_EtCC(ev_t_base, catc_to_test, T)

### SC scenario
ev_t_base_sc <- tribble(
  ~id, ~time, ~ii,  ~addl, ~dur,  ~cmt,  ~evid, ~Regimen,           ~Dose,
  1,   0,     336,  21,    0,     1,      1,     "1 mg/kg Q2W",     1
) %>% mutate(WTBL = unique(select(data_fin, USUBJID, WTBL)) %>% pull(WTBL) %>% median(), 
             LOG_WT = 0, LOG_CSF1 = 0, ADACAT = "0", ASSAY = "1",
             amt = Dose*WTBL, LDOSE = amt)

ets_cc_sc <- fun_EtCC(ev_t_base_sc, cc_to_test)
ets_catc_sc <- fun_EtCC(ev_t_base_sc, catc_to_test, T)
```

`r if (!knitr::is_html_output()) {'# Table of content'}`

```{r, eval=!knitr::is_html_output(), echo = FALSE}
officer::block_toc()
```

`r if (!knitr::is_html_output()) {'# List of figures'}`

```{r, eval=!knitr::is_html_output(), echo = FALSE}
officer::block_toc(seq_id = "Figure")
```

`r if (!knitr::is_html_output()) {'# List of tables'}`
```{r, eval=!knitr::is_html_output(), echo = FALSE}
officer::block_toc(seq_id = "Table")
```

\newpage
# Sensitivity of model parameters to covariate values 
```{r sensitivity-parameter-values}
fn_covsens_par <- str_c(path_to_save, "sim_covsens_par.Rdata")
if(!file.exists(fn_covsens_par) | overwrite){
  out_cov_par_sens <- bind_rows(
    fun_CovSens(ets_cc, covs_i = c(nice_names$COV, "LDOSE")) %>% mutate(Type = "Continuous"),
    fun_CovSens(ets_catc, covs_i = c(nice_names$COV, "LDOSE"), cat = T) %>% mutate(Type = "Categorical")
  ) %>% mutate(LAB = fct_inorder(LAB), Type = fct_inorder(Type))
  save(out_cov_par_sens, file = fn_covsens_par)
}
load(fn_covsens_par)

p_cov_sens_par <- ggplot(data = out_cov_par_sens, aes(x = LAB, y = mean, ymin = P025, ymax = P975, col = Type)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 0.8, ymax = 1.25, fill = "firebrick", alpha = 0.2) +
  geom_errorbar(width = 0.2) +
  geom_point(size = 2.5) +
  geom_hline(yintercept = 1, col = "grey25", lwd = 0.8, lty = "dashed") +
  geom_hline(yintercept = c(0.8, 1.25), col = "firebrick", lwd = 0.8, lty = "dotted") +
  scale_color_manual(values = MSDcol[c(1, 3, 4, 5, 6, 7)]) +
  scale_y_continuous(name = "Mean (95% CI) parameter\nchange from reference", breaks = scales::pretty_breaks(7)) +
  labs(x = NULL, caption = ds_cc_reflab) +
  facet_grid(VAR~., scales = "free") +
  coord_flip() +
  theme(legend.position = "top",
        legend.background = element_rect(fill = "white", size = 0.15, linetype = "solid", colour = "black"))
```

```{r p-sensitivity-parameter-values, fig.id = "p-sensitivity-parameter-values", fig.width = 10, fig.height = 6, fig.cap= if(knitr::is_html_output()) "Sensitivity of model parameters to covariate values"}
if (!knitr::is_html_output()) {
  block_caption("Sensitivity of model parameters to covariate values",
                style = "Figure Caption", autonum = run_num_fig)
}
p_cov_sens_par
```
grey dashed line - reference value (0% change); red dotted lines - 0.8 and 1.25-fold difference from the reference;  
confidence intervals built by sampling population parameters and beta coefficients from the uncertainty distribution (n = 1000).

```{r t-sensitivity-parameter-values, tab.cap= if(knitr::is_html_output()) "Summary of sensitivity of model parameters to covariate values", results = 'asis'}
t_cov_sens_par <- out_cov_par_sens %>% mutate_at(vars(mean:P975), signif, 3) %>% 
  mutate(`95%CI` = str_c(P025, ", ", P975), KEY = ifelse(is.na(KEY), "Category", KEY), BCOVVAL = as.character(BCOVVAL), BCOVVAL = ifelse(is.na(BCOVVAL), CATDES, BCOVVAL)) %>% 
  select(Parameter = VAR, Covariate = NICEN, `Cov. percentile` = KEY, `Cov. value` = BCOVVAL, Mean = mean, `95%CI`)

cat("<table width=100%>", paste0("<caption>", "(#tab:t-sensitivity-parameter-values)", "Summary of sensitivity of model parameters to covariate values", "</caption>"),"</table>", sep ="\n")

flextable(t_cov_sens_par) %>% set_table_properties(width = 1, layout = "autofit") %>% hline(part = "body")
```

# Sensitivity of exposure parameters to covariate values
## IV dosing
Simulated dosing schedule: 0.3 mg/kg Q2W IV; steady-state exposure parameters calculated at cycle `r ss_cycle` of consecutive treatment.  
```{r sensitivity-simulated-exposure}
fn_covsens_exp <- str_c(path_to_save, "sim_covsens_exp.Rdata")
if(!file.exists(fn_covsens_exp) | overwrite){
  out_cov_exp_sens <- bind_rows(
    fun_CovSens(ets_cc, covs_i = c(nice_names$COV, "LDOSE"), expos = T, stime_exp = stimes_ss) %>% mutate(Type = "Continuous"),
    fun_CovSens(ets_catc, covs_i = c(nice_names$COV, "LDOSE"), cat = T, expos = T, stime_exp = stimes_ss) %>% mutate(Type = "Categorical")
  ) %>% mutate(LAB = fct_inorder(LAB), Type = fct_inorder(Type))
  save(out_cov_exp_sens, file = fn_covsens_exp)
}
load(fn_covsens_exp)

p_cov_sens_exp <- ggplot(data = filter(out_cov_exp_sens, VAR != "Cmin, ug/mL"), aes(x = LAB, y = mean, ymin = P025, ymax = P975, col = Type)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 0.8, ymax = 1.25, fill = "firebrick", alpha = 0.2) +
  geom_errorbar(width = 0.2) +
  geom_point(size = 2.5) +
  geom_hline(yintercept = 1, col = "grey25", lwd = 0.8, lty = "dashed") +
  geom_hline(yintercept = c(0.8, 1.25), col = "firebrick", lwd = 0.8, lty = "dotted") +
  scale_color_manual(values = MSDcol[c(1, 3, 4, 5, 6, 7)]) +
  scale_y_continuous(name = "Mean (95% CI) parameter\nchange from reference", breaks = scales::pretty_breaks(7)) +
  labs(x = NULL, caption = ds_cc_reflab) +
  facet_grid(VAR~., scales = "free") +
  coord_flip() +
  theme(legend.position = "top",
        legend.background = element_rect(fill = "white", size = 0.15, linetype = "solid", colour = "black"))
```

```{r p-sensitivity-simulated-exposure, fig.id = "p-sensitivity-simulated-exposure", fig.width = 10, fig.height = 8, fig.cap= if(knitr::is_html_output()) "Sensitivity of simulated exposure to covariate values (IV dosing)"}
if (!knitr::is_html_output()) {
  block_caption("Sensitivity of simulated exposure to covariate values (IV dosing)",
                style = "Figure Caption", autonum = run_num_fig)
}
p_cov_sens_exp
```
grey dashed line - reference value (0% change); red dotted lines - 0.8 and 1.25-fold difference from the reference;  
confidence intervals built by sampling population parameters and beta coefficients from the uncertainty distribution (n = 1000).

```{r t-sensitivity-simulated-exposure, tab.cap= if(knitr::is_html_output()) "Summary of sensitivity of simulated exposure to covariate values (IV dosing)", results = 'asis'}
t_cov_sens_exp <- out_cov_exp_sens %>% mutate_at(vars(mean:P975), signif, 3) %>% 
  mutate(`95%CI` = str_c(P025, ", ", P975), KEY = ifelse(is.na(KEY), "Category", KEY), BCOVVAL = as.character(BCOVVAL), BCOVVAL = ifelse(is.na(BCOVVAL), CATDES, BCOVVAL)) %>% 
  select(Exposure = VAR, Covariate = NICEN, `Cov. percentile` = KEY, `Cov. value` = BCOVVAL, Mean = mean, `95%CI`)

cat("<table width=100%>", paste0("<caption>", "(#tab:t-sensitivity-simulated-exposure)", "Summary of sensitivity of simulated exposure to covariate values (IV dosing)", "</caption>"),"</table>", sep ="\n")

flextable(t_cov_sens_exp) %>% set_table_properties(width = 1, layout = "autofit") %>% hline(part = "body")
```
  
## SC dosing
Simulated dosing schedule: 1 mg/kg Q2W SC; steady-state exposure parameters calculated at cycle `r ss_cycle` of consecutive treatment.  
```{r sensitivity-simulated-exposure-sc}
fn_covsens_exp_sc <- str_c(path_to_save, "sim_covsens_exp_sc.Rdata")
if(!file.exists(fn_covsens_exp_sc) | overwrite){
  out_cov_exp_sens_sc <- bind_rows(
    fun_CovSens(ets_cc_sc, covs_i = c(nice_names$COV, "LDOSE"), expos = T, stime_exp = stimes_ss) %>% mutate(Type = "Continuous"),
    fun_CovSens(ets_catc_sc, covs_i = c(nice_names$COV, "LDOSE"), cat = T, expos = T, stime_exp = stimes_ss) %>% mutate(Type = "Categorical")
  ) %>% mutate(LAB = fct_inorder(LAB), Type = fct_inorder(Type))
  save(out_cov_exp_sens_sc, file = fn_covsens_exp_sc)
}
load(fn_covsens_exp_sc)

p_cov_sens_exp_sc <- ggplot(data = filter(out_cov_exp_sens_sc, VAR != "Cmin, ug/mL"), aes(x = LAB, y = mean, ymin = P025, ymax = P975, col = Type)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = 0.8, ymax = 1.25, fill = "firebrick", alpha = 0.2) +
  geom_errorbar(width = 0.2) +
  geom_point(size = 2.5) +
  geom_hline(yintercept = 1, col = "grey25", lwd = 0.8, lty = "dashed") +
  geom_hline(yintercept = c(0.8, 1.25), col = "firebrick", lwd = 0.8, lty = "dotted") +
  scale_color_manual(values = MSDcol[c(1, 3, 4, 5, 6, 7)]) +
  scale_y_continuous(name = "Mean (95% CI) parameter\nchange from reference", breaks = scales::pretty_breaks(7)) +
  labs(x = NULL, caption = ds_cc_reflab) +
  facet_grid(VAR~., scales = "free") +
  coord_flip() +
  theme(legend.position = "top",
        legend.background = element_rect(fill = "white", size = 0.15, linetype = "solid", colour = "black"))
```

```{r p-sensitivity-simulated-exposure-sc, fig.id = "p-sensitivity-simulated-exposure-sc", fig.width = 10, fig.height = 8, fig.cap= if(knitr::is_html_output()) "Sensitivity of simulated exposure to covariate values (SC dosing)"}
if (!knitr::is_html_output()) {
  block_caption("Sensitivity of simulated exposure to covariate values (SC dosing)",
                style = "Figure Caption", autonum = run_num_fig)
}
p_cov_sens_exp_sc
```
grey dashed line - reference value (0% change); red dotted lines - 0.8 and 1.25-fold difference from the reference;  
confidence intervals built by sampling population parameters and beta coefficients from the uncertainty distribution (n = 1000).

```{r t-sensitivity-simulated-exposure-sc, tab.cap= if(knitr::is_html_output()) "Summary of sensitivity of simulated exposure to covariate values (SC dosing)", results = 'asis'}
t_cov_sens_exp_sc <- out_cov_exp_sens_sc %>% mutate_at(vars(mean:P975), signif, 3) %>% 
  mutate(`95%CI` = str_c(P025, ", ", P975), KEY = ifelse(is.na(KEY), "Category", KEY), BCOVVAL = as.character(BCOVVAL), BCOVVAL = ifelse(is.na(BCOVVAL), CATDES, BCOVVAL)) %>% 
  select(Exposure = VAR, Covariate = NICEN, `Cov. percentile` = KEY, `Cov. value` = BCOVVAL, Mean = mean, `95%CI`)

cat("<table width=100%>", paste0("<caption>", "(#tab:t-sensitivity-simulated-exposure)", "Summary of sensitivity of simulated exposure to covariate values (SC dosing)", "</caption>"),"</table>", sep ="\n")

flextable(t_cov_sens_exp_sc) %>% set_table_properties(width = 1, layout = "autofit") %>% hline(part = "body")
```
  
  
# R Runtime Environment {.tabset}
## Current R session {.unnumbered}
```{r sourcefile}
source_file <- basename(rstudioapi::getSourceEditorContext()$path)
```

**Source file:** `r source_file`
```{r rsession, results='asis'}
# Print a record of the environment in which this script was rendered
info <- sessionInfo()
```

```{r tab-rsession-env}
# R Version
info$R.version %>%
  as.data.frame() %>%
  select(version.string, platform) %>%
  rename(
    `R version` = version.string,
    Platform = platform
  ) %>%
  flextable() %>%
  set_table_properties(width = 1, layout = "autofit")
```

## Base Packages {.unnumbered}
```{r tab-rsession-base}
# Base Packages
tibble(Package = info$basePkgs) %>%
  arrange(Package) %>%
  flextable() %>% 
  set_table_properties(layout = "autofit", width = 0.4)
```

## Attached Packages {.unnumbered}
```{r tab-rsession-attached}
# Attached Packages
info$otherPkgs %>%
  purrr::map_dfr(~ tibble(Package = .x$Package, Version = .x$Version)) %>%
  arrange(Package) %>%
  flextable() %>%
  set_table_properties(layout = "autofit", width = 0.4)
```

## Loaded Packages {.unnumbered}
```{r tab-rsession-loaded}
# Loaded Packages
info$loadedOnly %>%
  purrr::map_dfr(~ tibble(Package = .x$Package, Version = .x$Version)) %>%
  arrange(Package) %>%
  flextable() %>%
  set_table_properties(layout = "autofit", width = 0.4)
```

## {-}